\LARGE \bf Reactive Trajectory Planning and Trajectory Tracking for Pedestrian-Aware Autonomous Driving in Urban Environments

### 2016-01-22 root.tex
cleaned up FIXME sentence in paper
changed assosciation details
rearranging begun

\title{\LARGE \bf
  % Longitudinal Trajectory Planning and Tracking for Fixed-Path Autonomous Driving
  % Reactive Path Planning with Pedestrains for Autonomous Driving
  Reactive Trajectory Planning and Tracking Control for Pedestrian-Aware Autonomous Driving in Urban Environments
}

\author{
  Robert G. Cofield $^{1}$ and
  Rakesh Gupta $^{2}$
  \thanks{
    * This work was performed at Honda Research Institute USA.
  }
  \thanks{
    $^{1}$ Auburn University, Dept. of Mechanical Engineering, GPS \& Vehicle Dynamics Laboratory.
  }
  \thanks{
    $^{2}$ Honda Research Institute USA Inc, 375 Ravendale Drive, Mountain View, CA 94043. rgupta@hra.com
  }
}

@@

In this paper, we address the problem of trajectory planning for urban roads while being 
reactive to the presence of pedestrians.
Past work reduces jerk and limits velocities and acceleration to smooth trajectories, but it does not consider 
reactive behaviors such as responding to pedestrians. On the other hand, systems for collision 
avoidance, plan paths around obstacles and pedestrians, stop for them, or produce a warning. 
In this paper, we present an integrated trajectory generation and tracking control system for urban 
environments that simultaneously considers constraints to maximize human comfort and real-time  
trajectory updates to react to pedestrians on the road.

Given a desired path, we present a novel online method for planning longitudinal trajectories 
to follow the urban path with turns and intersections while honoring traffic regulations such 
as stop signs. Based on sensor data, our method updates the trajectory plan to safely avoid 
pedestrians on the road by slowing or stopping.
Our method has closed form solutions, and runs at 20 Hz, and is efficient and reliable 
for use in online planning. We have confirmed this with
a test vehicle and pedestrians with 10s of hours of testing under autonomous driving conditions.

@@

We first describe the architecture of our system in Section II. We also describe other subsystems that our system needs to work with, and planned stops.
In Section III, we describe trajectory planning which takes a 2D path and generates a trajectory that satisfies jerk and maximum velocity and acceleration constraints. 
We explain how we handle intersections, turns in the road and planned stops due to stop signs (that have already been marked in the map).
We then describe extensions to trajectory planner that handle reactivity to pedestrians in the environment. 
Once a trajectory plan is formulated, it must be utilized online to send the reference signal to the controllers that govern steering, braking, and engine speed.
This is the trajectory tracking problem, which is discussed in Section \ref{sec:trajectorytracking}.
Section V describes the high level Path Manager that calls the trajectory planner as necessary to 
exhibit reactionary behavior and stop for pedestrians that may appear on the road.
We then conclude and discuss future extensions.
% tracking

@@

\section{System Architecture} \label{sec:systemarchirectureg}

Our system architecture is shown in Figure \ref{fig:addreact}.
There are 4 primary input components.
A path planner determines the optimal course to take by searching a map database.
This same map database is used to search for stop signs and provide their locations.
A GPS/INS navigation filter provides estimates of global position, velocity vector, attitude, and acceleration.
A pedestrian detection component \cite{Gepperth2013,Gepperth2014} leverages computer vision in conjunction with the navigation filter to estimate the global location of pedestrians which are walking in front of the vehicle.
Techniques for designing these components are abundant in the literature and are addressed here.

@@

We assume that we have access to Path Planner. For example, this can be a service similar to
Google Maps except that it provides lane level maps. 
We assume that the path planner operates independently from the trajectory planner and tracker.
We also assume that we have a High
Resolution digital map with Lane centers, Stop signs, crosswalk geometry, and Turning 
curves at intersections. The starting position the 
car is determined via high grade GPS. The destination is manually input into the system.
Using the path planner, we obtain a path along lane centers from start to the destination.
This plan is output as waypoints, with the waypoints corresponding to stop signs marked.

@@

@@

Pedestrian Detection is performed via a Camera, and LiDAR system. It computes a bounding 
box for each pedestrian as shown in Figure \ref{fig:ped}. The pedestrian position is 
transformed to the vehicle body frame, and subsequently transformed to global frame to be related to the planned path.

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.3\columnwidth]{graphics/IntersectionCrosswalks.png}
  \caption{A car turning right at the intersection only needs to care about pedestrians in the 
pedestrian crossings shown yellow. Pedestrians in the green crossings can be ignored unless they
appear somewhere on the road}
  \label{fig:intersect}
\end{figure}

We also have an In-Out Algorithm implemented via polygon intersection that can be used to
ignore “safe” pedestrians that are on sidewalks, off-path crosswalks, and behind planned stop
as shown in Figure \ref{fig:intersect}.
Remaining pedestrians pose collision risk and we need to reactively slow down or stop for them.
This is accomplished by sending stop message with pedestrian locations to path manager.

For Navigation Filtering we use an ADMA-G based Commercial automotive GPS/INS system.
It receives RTK corrections via cell modem.
It outputs Global position, global heading,
body frame velocity and body frame acceleration to cm. level accuracy.

@@

% make sure to incorporate extensibility to other constraints
The goal of the segmentation process is to divide a given path into multiple portions where each has a uniform upper limit on speed, acceleration, and braking.
There are 3 steps in the segmentation process:
\begin{enumerate} \label{asdf}
  \item \emph{Ceiling calculation}, where $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$ are found for every point in the given path.
  \item \emph{Clustering}, in which path points are grouped sequentially.
  \item \emph{Consolidation}, in which a single $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$ is selected for each segment.
\end{enumerate}
After this is done, the process described above in Section \ref{sec:jerkprofiles} may be applied to each of the segments.

@@

\section{Trajectory Tracking Control} \label{sec:trajectorytracking}

@@

The assumption on our work is that there is a unique mapping from a reference time $t_{ref}$ to a scalar value indicating the distance along the current path, $s$.
system.
This mapping breaks down when we are stopped at a planned or reactive stop, as there is no way to do a $t_{ref}(s)$ lookup when multiple reference time solutions exist for certain path positions.
The solution is to break the path into sub-paths at each stop location (i.e., stop sign) which is known a priori, and plan then execute them incrementally as shown in Fig. \ref{fig:segmentation}.
This is the first function of the path manager, and can be broken down as follows:
\begin{itemize}
\item Send first sub-path to trajectory planner
\item Wait until completed.
\item Pause for fixed time, typically 2-3 second.
\item Continue waiting if any pedestrians are in the roadway ahead (along the intended path) within some fixed distance.
\item Send next sub-path to planner.
\item Repeat until end of path is reached.
\end{itemize}

\begin{figure}[thpb]
\centering
  \subfigure[In NORMAL mode, RSTOP is now triggered.]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_NORMAL_time_to_stop.png}}
  \\
  \subfigure[RSTOP diagram showing bounds for revising the RSTOP trajectory.]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_Replan.png}}
  \\
  \subfigure[PSTOP diagram showing bounds for reverting to NORMAL mode.]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_Resume.png}}
  \caption{Reactive behavior to pedestrian}
  \label{fig:react}
\end{figure}
\emph{RG: a figure text etc is smaller than b and c. maybe crop from right to make same size}

>>>>

\title{\LARGE \bf
  % Longitudinal Trajectory Planning and Tracking for Fixed-Path Autonomous Driving
  % Reactive Path Planning with Pedestrains for Autonomous Driving
  Reactive Trajectory Planning and Trajectory Tracking for Pedestrian-Aware Autonomous Driving in Urban Environments
}

\author{
  Robert G. Cofield $^{1}$ and
  Rakesh Gupta $^{2}$
  \thanks{
    * This work was performed at Honda Research Institute USA.
  }
  \thanks{
    $^{1}$ Auburn University GAVLab. 1418 Wiggins Hall, Auburn, AL 36832. robertgcofield@gmail.com
  }
  \thanks{
    $^{2}$ Honda Research Institute USA Inc, 375 Ravendale Drive, Mountain View, CA 94043. rgupta@hra.com
  }
}

@@

In this paper, we address the problem of trajectory planning for urban roads while reacting to the presence of pedestrians.
Past work reduces jerk and limits velocities and acceleration to smooth trajectories, but it does not consider reactive behaviors such as responding to pedestrians.
On the other hand, systems for collision avoidance plan paths around obstacles and pedestrians, stop for them, or produce a warning. 
In this paper, we present an integrated trajectory generation and tracking system for urban environments that simultaneously considers constraints to maximize human comfort and real-time trajectory updates to react to pedestrians on the road.

Given a desired path, we present a novel online method for planning longitudinal trajectories to follow the urban path with turns and intersections while honoring traffic regulations such as stop signs.
Based on sensor data, our method updates the trajectory plan to safely avoid pedestrians on the road by slowing or stopping.
This is critical in urban environments, when modifying the vehicle's intended path is often not possible.
Our method has closed form solutions, runs at 20 Hz, and is efficient and reliable for use in online planning.
We have confirmed this with a test vehicle and pedestrians with over 100 hours of testing under driverless operation.

@@

We first describe the architecture of our system in Sec. \ref{sec:systemarchirecture}.
We also describe other subsystems that our system needs to work with, and planned stops.
In Section \ref{sec:trajectoryplanning}, we describe trajectory planning which takes a 2D path and generates a trajectory that satisfies jerk and maximum velocity and acceleration constraints. 
We explain how we handle intersections, turns in the road and planned stops due to stop signs (that have already been marked in the map).
We then describe extensions to trajectory planner that handle reactivity to pedestrians in the environment. 
Once a trajectory plan is formulated, it must be utilized online to send the reference signal to the controllers that govern steering, braking, and engine speed.
This is the trajectory tracking problem, which is discussed in Section \ref{sec:trajectorytracking}.
Section V describes the high level Path Manager that calls the trajectory planner as necessary to 
exhibit reactionary behavior and stop for pedestrians that may appear on the road.
We then conclude and discuss future extensions.
% tracking

@@

\section{System Architecture} \label{sec:systemarchirecture}

Our system architecture is shown in Figure \ref{fig:addreact}.
There are 4 primary input components: a path planner, navigation filter, pedestrian detector, and a map which provides the location of stop signs.
% nav filter
For navigation filtering we use an ADMA-G  commercial automotive GPS/INS system.
It receives RTK corrections via cell modem.
It outputs global position, global heading, body frame velocity and body frame acceleration to centimeter level accuracy.

@@

Pedestrian detection is performed via a camera and LiDAR system based on \cite{Gepperth2013,Gepperth2014}.
It computes a bounding box for each pedestrian as shown in Figure \ref{fig:ped}.
The pedestrian position is transformed to the vehicle body frame, and subsequently transformed to global frame to be related to the planned path.

@@

We assume that we have access to a path planner.
For example, this can be a service similar to Google Maps except that it provides lane level maps. 
We assume that the path planner operates independently from the trajectory planner and tracker.
We also assume that we have a high resolution digital map with lane centers, stop signs, crosswalk geometry, and turning curves at intersections.
The destination is manually input into the system by the passengers.
Using the path planner, we obtain a path along lane centers from the vehicle's current location (computed by the navigation filter) to the destination.
This plan is output as set of global waypoints, with the waypoints corresponding to stop signs flagged.
This same map database is used to search for stop signs and provide their locations.

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.3\columnwidth]{graphics/IntersectionCrosswalks.png}
  \caption{
    A car turning right at the intersection only needs to consider pedestrians in the pedestrian crossings shown yellow.
    Pedestrians in the green crossings can be ignored unless they appear somewhere on the road.
  }
  \label{fig:intersect}
\end{figure}

We also have an In-Out Algorithm implemented via polygon intersection that can be used to ignore “safe” pedestrians
Pedestrians that are on sidewalks, off-path crosswalks, and behind planned stops as shown in Figure \ref{fig:intersect} can be considered ``safe'' and are ignored.
This is done by searching the same map database used for path planning.
Remaining pedestrians pose collision risk and the vehicle needs to reactively slow down or stop for them.
This is accomplished by sending stop message with pedestrian locations to the path manager.

Beyond the input subsystems, there are three other major components: a high-level planner, a low-level planner, and a software controller which governs engine speed, braking, and steering.
The controller takes as an input a trajectory which is sampled at 10 Hz and spans 2 seconds, beginning at the moment of data transmission.
This short-term trajectory is oriented in the vehicle body frame.
\textbf{Citation for controller !!!!!}.
The function of the low-level planner (``trajectory planner'') is two-fold:
\begin{itemize}
  \item Compute medium-range trajectories, as detailed in Sec. \ref{sec:trajectoryplanning}.
  \item Sample medium-range trajectories for input to the controller, as detailed in Sec. \ref{sec:trajectoryplanning}
\end{itemize}

This work focuses on the high- and low-level planners.

The assumption on our work is that there is a unique mapping from a reference time $t_{ref}$ to a scalar value indicating the distance along the current path from the starting, $s$.
system.
This mapping breaks down when the vehicle is stopped (planned or unplanned), as there is no way to look up $t_{ref}(s)$ when multiple reference time solutions exist for certain path positions.
The solution is to break the path into sub-paths at each stop location (i.e., stop sign) which is known a priori, and plan then execute them incrementally as shown in Fig. \ref{fig:segmentation}.
This is the first function of the path manager.
% , and can be broken down as follows:
% \begin{itemize}
% \item Send first sub-path to trajectory planner
% \item Wait until completed.
% \item Pause for fixed time, typically 2-3 second.
% \item Continue waiting if any pedestrians are in the roadway ahead (along the intended path) within some fixed distance.
% \item Send next sub-path to planner.
% \item Repeat until end of path is reached.
% \end{itemize}

\begin{figure}[thpb]
\centering
  \subfigure[In NORMAL mode, RSTOP is now triggered.]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_NORMAL_time_to_stop.png}}
  \\
  \subfigure[RSTOP diagram showing bounds for revising the RSTOP trajectory.]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_Replan.png}}
  \\
  \subfigure[PSTOP diagram showing bounds for reverting to NORMAL mode.]{\includegraphics[width=1.0\columnwidth]{graphics/RSTOP_Resume.png}}
  \caption{Reactive behavior to pedestrian}
  \label{fig:react}
\end{figure}

@@

% make sure to incorporate extensibility to other constraints
The goal of the segmentation process is to divide a given path into multiple portions where each has a uniform upper limit on speed, acceleration, and braking.
There are 3 steps in the segmentation process:
\begin{enumerate} \label{asdf}
  \item \emph{Ceiling calculation}, where $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$ are found for every point in the given path.
  \item \emph{Clustering}, in which path points are grouped sequentially.
  \item \emph{Consolidation}, in which a single $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$ is selected for each segment.
\end{enumerate}
After this is done, the process described in Section \ref{sec:jerkprofiles} may be applied to each of the segments.

@@

\section{Trajectory Tracking} \label{sec:trajectorytracking}

@@
